The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-17 paper.tex
update

  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect\
  on the overall morphology of the \textit{Fermi} bubbles,\
  but only sharpens the edges of the simulated bubbles by the interplay between magnetic fields\
  and anisotropic CR diffusion with suppressed perpendicular diffusion across the bubble surface. Moreover,\
  the magnetic fields within the \textit{Fermi} bubbles should be weak due to\
  adiabatic expansion, and thus the fields has\
  a little effect on the overall dynamics.

@@

\section{Acknowledgements}
The authors thank Mateusz Ruszkowski and Ellen G. Zweibel for insightful comments.\
We thank Peter Predehl for providing the range of observed X-ray intensity in \Cref{fig__xray_0.8keV_angle_000}.\
A part of the simulations are performed and analyzed using computing facilities\
operated by the national center for High Performance Computing.
HYKY acknowledge support from\
Yushan Scholar Program of the Ministry of Education of Taiwan\
and\
Ministry of Science and Technology of Taiwan (MOST 109-2112-M-007-037-MY3).
HS acknowledges\
funding support from the Jade Mountain Young Scholar Award No. NTU-109V0201,\
sponsored by the Ministry of Education, Taiwan.\
This research is partially supported by the Ministry of Science and\
Technology of Taiwan (MOST) under grants MOST 107-2119-M-002-036-MY3\
and MOST 108-2112-M-002-023-MY3, and the NTU\
Core Consortium project under grants NTU-CC-108L893401 and\
NTU-CC-108L893402.

>>>>

  As stressed by \citet{Yang2012}, CR diffusion has an insignificant effect\
  on the overall morphology of the \textit{Fermi} bubbles,\
  but only sharpens the edges of the simulated bubbles by the interplay between magnetic fields\
  and anisotropic CR diffusion with suppressed perpendicular diffusion across the bubble surface.

  Moreover, the magnetic fields within the \textit{Fermi} bubbles should be weak due to\
  adiabatic expansion, and thus the fields has\
  a little effect on the overall dynamics.

@@

\section{Acknowledgements}
The authors thank Mateusz Ruszkowski and Ellen G. Zweibel for insightful comments.\
We thank Peter Predehl for providing the range of observed X-ray intensity in \Cref{fig__xray_0.8keV_angle_000}.\
A part of the simulations are performed and analyzed using computing resources\
operated by the national center for High Performance Computing.
HYKY acknowledge support from\
Yushan Scholar Program of the Ministry of Education of Taiwan\
and\
Ministry of Science and Technology of Taiwan (MOST 109-2112-M-007-037-MY3).
HS acknowledges\
funding support from the Jade Mountain Young Scholar Award No. NTU-109V0201,\
sponsored by the Ministry of Education, Taiwan.\
This research is partially supported by the Ministry of Science and\
Technology of Taiwan (MOST) under grants MOST 107-2119-M-002-036-MY3\
and MOST 108-2112-M-002-023-MY3, and the NTU\
Core Consortium project under grants NTU-CC-108L893401 and\
NTU-CC-108L893402.
